Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-11 ms.Rnw
typo

Goodness-of-fit alone does not guarantee that a model provides a correct causal interpretation of the model.
Indeed, associative models are not constrained to have a causal interpretation, and typically are designed with the sole goal of providing a statistical fit to data.
Consequently, we should not require a candidate mechanistic model to beat all benchmarks.
However, a mechanistic model which falls far short against benchmarks is evidently failing to explain some substantial aspect of the data.
A convenient measure of fit should have interpretable differences that help to operationalize the meaning of far short.
Ideally, the measure should also have favorable theoretical properties.
Consequently, we focus on log-likelihood as a measure of goodness of fit, and we adjust for the degrees of freedom of the models to be compared by using Aka-Ike's information criterion (AIC).

>>>>

Goodness-of-fit alone does not guarantee that a model provides a correct causal interpretation of the model.
Indeed, associative models are not constrained to have a causal interpretation, and typically are designed with the sole goal of providing a statistical fit to data.
Consequently, we should not require a candidate mechanistic model to beat all benchmarks.
However, a mechanistic model which falls far short against benchmarks is evidently failing to explain some substantial aspect of the data.
A convenient measure of fit should have interpretable differences that help to operationalize the meaning of far short.
Ideally, the measure should also have favorable theoretical properties.
Consequently, we focus on log-likelihood as a measure of goodness of fit, and we adjust for the degrees of freedom of the models to be compared by using the Akaike information criterion (AIC) \eic{REF}.
